On the Use of K-Competitive Networks \\ for Writing Style Transfer

### 2017-12-02 dl_style_transfer/paper/main.tex
Updated paper

\begin{abstract}
Writing style is a key component of the quality of any online review - a detailed and informative review is only useful insofar as it is able to retain a reader's attention. In this paper, we explore the use of $k$-competitive layers in convolutional neural networks to classify the author of a given piece of text. We then apply the techniques used in neural style transfer for images to transfer the writing style of one author onto the content written by another. Given sufficient examples of well-written reviews, our techniques can be used to globally improve the quality of reviews on Yelp.
\end{abstract}

@@

\cite{Edirisooriya} and \cite{Kabbara16} both consider a similar method to ours in terms of generating style and content representations of text, and \cite{Kabbara16} defines three evaluation criteria: soundness (preservation of content), coherence (grammatical correctness \& common sense), and effectiveness (matches intended style). However, these lack sufficient experiments with which to evaluate the quality of their results.

>>>>

\begin{abstract}
Writing style is a key component of the quality of any online review - a detailed and informative review is only useful insofar as it is able to retain a reader's attention. In this paper, we explore the use of $k$-competitive layers in convolutional neural networks to classify the author of a given piece of text. We then apply the techniques used in neural style transfer for images to transfer the writing style of one author onto the content written by another. Given sufficient examples of well-written reviews, our techniques can be used to improve the quality of reviews on online platforms such as Yelp or Amazon.
\end{abstract}

@@

\cite{Edirisooriya} and \cite{Kabbara16} both consider a similar method to ours in terms of generating style and content representations of text, and \cite{Kabbara16} defines three evaluation criteria: soundness (preservation of content), coherence (grammatical correctness \& common sense), and effectiveness (matches intended style). However, these lack sufficient experiments with which to evaluate the quality of their results. \cite{Fu17} provides a quantitative assessment of their content and style representations, in addition to a more complex alternative architecture. All of the aforementioned works use a recurrent neural network encoder-decoder structure (otherwise referred to as a ``seq2seq'' model), with either a long short-term memory (LSTM) or gated recurrent unit (GRU) used as the underlying structure. These methods seek to encode the content of the input text into a low dimensional space, and then use the decoder to generate text in a specified style. Our key contribution is in the use of convolutional neural networks, which have proven very successful at tasks such as sentiment analysis \cite{Kim14f}.
